Coupling finite and boundary element methods to solve the Poisson--Boltzmann equation for electrostatics in molecular solvation

### 2023-09-20 reply_to_referees.txt

The authors propose a combination of FEM and BEM (FEM-BEM) to leverage the advantages of both methods. This approach shows promise and could be valuable if a robust software package is developed. However, significant changes are required for this work to meet the standard in the field. My concerns are outlined below.

Reply:
We thank this reviewer for the careful revision. We are glad to see that this reviewer appreciates the potential of our work, and we hope that the substantial changes in this new version satisfy his/her concerns.

Comment 1: 
A comparison of the Kirkwood sphere can be found in the following reference: 'Treatment of charge singularities in implicit solvent models', The Journal of Chemical Physics, 127, 114106, 2007. In this work, four different cases were studied, involving up to six charges, and convergence orders were reported almost 20 years ago.

Reply:
As the reviewer points out, in that reference there is a comparison with the Kirkwood sphere for various charge distributions (with up to 6 charges). In the original version of the manuscript we also included this test case, however, considering four rather than six charges. In this test case, one of the charges was placed 1 Å away from the surface, which, according to that same reference, is a challenging setup, and showed the correct order of convergence. We don't think that performing a study similar to the cited paper would add more information to the reader.

However, we thank the reviewer for pointing us to this reference, and we apologize for missing it in the original manuscript. We have added it to the new version.

@@

Examining the consistency over different mesh sizes is also a standard approach in the field. For many poorly designed methods, this poses a severe challenge, and many researchers simply refuse to engage in this pursuit, ultimately making no progress in solving the PB problem despite years of struggle. I suggest the authors examine the proposed FEM-BEM method using a set of 153 biomolecules, as was done in the study titled 'Accurate, Robust, and Reliable Calculations of Poisson-Boltzmann Binding Energies' published in the Journal of Computational Chemistry, 2017, 38, 941–948. In fact, Fenley and coworkers initially proposed this challenge. It is interesting for the authors to compare the performance of their method with that of the aforementioned JCC paper.

Reply:
We thank the reviewer for this comment, and his/her concern to enhance the robustness of our work. As suggested by the reviewer, we examined the JCC paper and went on to perform the calculations for the 153 structures, with the corresponding binding energy results. Biding energies are extremely challenging, as there are small differences between much larger solvation energies, making accuracy key. Inspired by a previous result reported in the original manuscript, we chose a mesh refinement with low enough error in the solvation energy to perform the binding energy calculations on the data set. We extracted the results from the JCC paper suggested by the reviewer, and a previous JCTC paper by Harris, Boschitsch, and Fenley (9, 3677, 2013) that runs the same data set, to compare our results against APBS, MIBPB, CPB, PBSA, and Delphi. We saw that in all cases our results were within the range of the other software, evidencing code correctness.

We would like to note that some of the 153 structures of the data set had cavities where water molecules can fit. In a finite difference description, these regions are naturally considered as having the bulk water permittivity. Then, we had to consider them accordingly to make an appropriate comparison with the other codes. This meant that we had a variable permittivity inside the molecular region, which is one of the motivations behind this work, making our point of using FEM in the molecule more compelling.

@@

Preamble:
This paper presents a novel FEM-BEM method for approximating the solution to the linearized Poisson-Boltzmann equation.  The authors provide a good overview of their methodology with useful comparisons to results obtained with the APBS software package.  The paper is a useful contribution, but should be revised before it is published.

Reply:
We truly appreciate the work of the reviewer and are happy to see he/she considers it a useful contribution.

Comment 1:
1) It should be more clear that the methodology presented in this paper is for the linearised Poisson-Boltzmann equation (LPBE) that results from approximating sinh(x) with x.  The Poisson-Boltzmann equation (PBE) can be found in many of the cited papers, including https://doi.org/10.1073/pnas.181342398

Reply:
The reviewer is completely correct, and we apologize for not making this point clearer in the original manuscript. We have edited it accordingly.

@@

Modifications:
We have added linearised phrase in the abstract, a sentence in 'We are proposing a coupling scheme for the linear Poisson-Boltzmann equation.' in the introduction and a sentence ' The linearised Poisson-Boltzmann equation that results from approximating $\sinh(x)$ with $x$ follows' in the methodology to clarify the equation considered.

Comment 2:
2) That said, providing a fast method for solving the LPBE is still very useful for many reasons including: (a) Newton-based solvers for the PBE solve the LPBE at each step, (b) for many problems approximating sinh(x) by x does not introduce a large error.  However, the authors should still be clear that they are solving the LPBE and not the PBE, and/or they should extend the discussion/algorithm/results to include the PBE.

Reply:
Although we agree with the reviewer that we were not clear enough that the linear version was being solved and that solving the nonlinear PBE is extremely important, we believe that adding results that include the nonlinear PBE is out of the scope of the current manuscript. In fact, this was the original motivation behind developing our FEM-BEM coupled approach, as BEM cannot solve the nonlinear equation, which is why we mention this in the introduction. However, in the development process, we realied there are several milestones that need to be reached before coupling FEM and BEM for the nonlinear problem, and this work is the first step that will take us there. Then, this comment points to future directions of development.

### 2023-09-20 intro.tex
Linear PBE - comment
Changes to clarify that we consider linearised version of PBE.
small edits

The present article describes a methodology to overcome some of those limitations, by coupling finite and boundary element methods.
This approach brings the best of both worlds---the flexibility of FEM and the efficiency of BEM---all in an accurate description of the solute molecule.
FEM-BEM coupling is a popular technique in the context of mixed linear-nonlinear models,\cite{carstensen1995coupling,aurada2013classical} fracture mechanics,\cite{aour2007coupled} fluid-structure interaction,\cite{estorff1991fem} acoustics,\cite{hiptmair2006stabilized} and electromagnetics.\cite{matsuoka1988calculation,hiptmair2008stabilized,bruckner20123d}
On the other hand, the PBE has been solved with hybrid numerical methods in the past: for example, by coupling finite differences with boundary elements\cite{boschitsch2004hybrid} or finite elements\cite{xie2016new,ying2018hybrid} to solve the nonlinear PBE in a specific region, and to implement modifications to the PBE model (i.e. the size-modified PBE).
To the best of our knowledge, this is the first time finite and boundary elements have been combined in this application.

In this paper, we prototype this principle with the simplest implementation possible: a Johnson--N\'ed\'elec\cite{johnson1980coupling} coupling, where we solve using mass-matrix and diagonal preconditioning and without distributed memory execution.
This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in open-source software libraries.
In this work, we use the boundary element library Bempp-cl\cite{BetckeScroggs2021} and the finite element library FEniCSx\cite{BasixJoss,BasixDofTransformations}.
These libraries are easy to use and their full functionalities may be accessed via their Python interfaces, making them ideal tools for easily implementing problems like this as well as for exploring computational efficiency and moving towards tackling large-scale problems, such as a full viral capsid.\cite{MartinezETal2019,wang2021high}
We hope this work will inspire research along these lines.

>>>>

The present article describes a methodology to overcome some of those limitations, by coupling finite and boundary element methods.
This approach brings the best of both worlds---the flexibility of FEM and the efficiency of BEM---all in an accurate description of the solute molecule.
FEM-BEM coupling is a popular technique in the context of mixed linear-nonlinear models,\cite{carstensen1995coupling,aurada2013classical} fracture mechanics,\cite{aour2007coupled} fluid-structure interaction,\cite{estorff1991fem} acoustics,\cite{hiptmair2006stabilized} and electromagnetics.\cite{matsuoka1988calculation,hiptmair2008stabilized,bruckner20123d}
On the other hand, the PBE has been solved with hybrid numerical methods in the past: for example, by coupling finite differences with boundary elements\cite{boschitsch2004hybrid} or finite elements\cite{xie2016new,ying2018hybrid} to solve the nonlinear PBE in a specific region, and to implement modifications to the PBE model (i.e. the size-modified PBE).
To the best of our knowledge, this is the first time finite and boundary elements have been combined in this application. We are proposing a coupling scheme for the linear Poisson-Boltzmann equation.

In this paper, we prototype this principle with the simplest implementation possible: a Johnson--N\'ed\'elec\cite{johnson1980coupling} coupling, where we solve using mass-matrix and diagonal preconditioning, and without distributed memory execution.
This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in open-source software libraries.
In this work, we use the boundary element library Bempp-cl\cite{BetckeScroggs2021} and the finite element library FEniCSx\cite{BasixJoss,BasixDofTransformations}.
These libraries are easy to use and their full functionalities may be accessed via their Python interfaces, making them ideal tools for easily implementing problems like this as well as for exploring computational efficiency and moving towards tackling large-scale problems, such as a full viral capsid.\cite{MartinezETal2019,wang2021high}
We hope this work will inspire research along these lines.

### 2023-09-20 main.tex
small edits

\subsection*{\sffamily \large ACKNOWLEDGMENTS}
MB acknowledges the support from Kingston University through the First Kingston University Grant. \\
MS acknowledges support from EPSRC grant EP/W007460/1 \\
TB acknowledges support from EPSRC grants EP/W007460/1 and EP/W026260/1. \\
EB acknowledges support from EPSRC grants EP/V050400/1 and EP/W007460/1. \\
CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.\\
We would like to thank J{\o}rgen Dokken for his help with various implementation details related to FEniCSx.
%((Place Acknowledgments here))

>>>>

\subsection*{\sffamily \large ACKNOWLEDGMENTS}
MB acknowledges the support from Kingston University through the First Kingston University Grant. \\
MS acknowledges support from EPSRC grant EP/W007460/1 \\
TB acknowledges support from EPSRC grants EP/W007460/1 and EP/W026260/1. \\
EB acknowledges support from EPSRC grants EP/V050400/1 and EP/W007460/1. \\
CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004 and Universidad T\'ecnica Federico Santa Mar\'ia through Proyectos Internos USM 2023 PI-LIR-23-03.\\
We would like to thank J{\o}rgen Dokken for his help with various implementation details related to FEniCSx.
%((Place Acknowledgments here))

### 2023-09-20 methods.tex
small edits

A common quantity of interest in implicit solvent models is the solvation free energy, which is the change in Gibbs free energy as the molecule moves from the vacuum into the solvent. Considering the charge distribution $\rho$ consists of point charges, this can be calculated as
%
\begin{equation}\label{eq:dG} 
\Delta G_{\text{solv}} = \tfrac{1}{2}\int_{\Omega_1} \rho(\mathbf{x})\phi_{r}(\mathbf{x}) = \tfrac{1}{2}\sum_{k=1}^{N_q} q_k\phi_r(\mathbf{x_k}).
\end{equation}

@@

Several possible boundary integral formulations of \eqref{eq:pbe} exist.~\cite{search2022towards} The simplest form was presented by Yoon and Lenhoff in 1991\cite{YoonLenhoff1990} and is known as the \emph{direct formulation}. However, the resulting system is usually ill-conditioned. Here, we use the better-conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006, LuETal2009,debuhr2016dashmm} which reads
%
\begin{align}\label{eq:lu}
    \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 &= \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},
     \nonumber \\
    \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 &= \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),
\end{align}
where $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ is the potential on $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Dirichlet trace),
and $\lambda_2 = \frac{\partial}{\partial \mathbf{n}}\phi_2$ is the normal derivative $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Neumann trace).
Note that we can obtain $\phi_1$ and $\lambda_1$ from $\phi_2$ and $\lambda_2$ by applying the interface conditions \eqref{eq:pbe3} and \eqref{eq:pbe4}.
The operators $V$, $K$, $K^{\prime}$, and $W$ that appear in Equation \eqref{eq:lu} are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels. These are defined %in Equation~\eqref{eq:single_double} and 
by
%
\begin{align}\label{eq:all_op}
V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',
\end{align}
%
where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and %Green's functions $g_L, g_Y$ were defined in Equation~\eqref{eq:green_func}.
\begin{align}\label{eq:green_func}
g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
\end{align}
are the corresponding free-space Green's functions.

@@

The boundary element method (BEM) is a standard tool for the numerical solution of the linear version of the Poisson--Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,cooper2016pygbe} and more recently, with Bempp-cl\cite{search2022towards}. One strong advantage of BEM is that it reduces the dimension of the problem by using the boundary integral formulation. Unfortunately, this advantage comes at a cost: it requires a fundamental solution to be known in order for the method to be applied. There are many linear problems for which fundamental solutions are not known: this is the case for the Poisson-Boltzmann equation with a heterogenous permittivity inside the molecule, \emph{ie}.
%
\begin{align} \label{eq:pbe_vp}
\nabla \cdot \left(\epsilon_1(\mathbf{x}) \nabla \phi_1(\mathbf{x})\right) &= \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) &&\mathbf{x} \in \Omega_1,\nonumber\\
\left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0 &&\mathbf{x}\in\Omega_2,\nonumber\\
\phi_1(\mathbf{x})  &= \phi_2(\mathbf{x}),&&\mathbf{x}\in \Gamma,\nonumber\\
\epsilon_1(\mathbf{x})\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x})  &= \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x}) &&\mathbf{x}\in \Gamma. 
\end{align}
%
A finite element method (FEM) is more suitable for such a case.

>>>>

A common quantity of interest in implicit solvent models is the polar component of the solvation free energy, which is the change in Gibbs free energy as the molecule charges move from vacuum into a solute-shaped cavity inside the solvent. Considering the charge distribution $\rho$ consists of point charges, this can be calculated as
%
\begin{equation}\label{eq:dG} 
\Delta G_{\text{solv}} = \tfrac{1}{2}\int_{\Omega_1} \rho(\mathbf{x})\phi_{r}(\mathbf{x}) = \tfrac{1}{2}\sum_{k=1}^{N_q} q_k\phi_r(\mathbf{x_k}).
\end{equation}

@@

Several possible boundary integral formulations of \eqref{eq:pbe} exist.~\cite{search2022towards} The simplest form was presented by Yoon and Lenhoff in 1991\cite{YoonLenhoff1990} and is known as the \emph{direct formulation}. However, the resulting system is usually ill-conditioned. Here, we use the better-conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006, LuETal2009,debuhr2016dashmm} which reads
%
\begin{align}\label{eq:lu}
    \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 &= \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},
     \nonumber \\
    \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 &= \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),
\end{align}
where $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ is the potential on $\Gamma$ as we approach from $\Omega_2$ ({\it i.e.} the exterior Dirichlet trace),
and $\lambda_2 = \frac{\partial}{\partial \mathbf{n}}\phi_2$ is the normal derivative $\Gamma$ as we approach from $\Omega_2$ ({\it i.e.} the exterior Neumann trace).
Note that we can obtain $\phi_1$ and $\lambda_1$ from $\phi_2$ and $\lambda_2$ by applying the interface conditions \eqref{eq:pbe3} and \eqref{eq:pbe4}.
The operators $V$, $K$, $K^{\prime}$, and $W$ that appear in Equation \eqref{eq:lu} are the single-layer, double-layer, adjoint double-layer, and hypersingular operators, respectively, for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels. These are defined %in Equation~\eqref{eq:single_double} and 
by
%
\begin{align}\label{eq:all_op}
V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',
\end{align}
%
where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and %Green's functions $g_L, g_Y$ were defined in Equation~\eqref{eq:green_func}.
\begin{align}\label{eq:green_func}
g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
\end{align}
are the corresponding free-space Green's functions.

@@

The boundary element method (BEM) is a standard tool for the numerical solution of the linear version of the Poisson--Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,cooper2016pygbe} and more recently, with Bempp-cl\cite{search2022towards}. One strong advantage of BEM is that it reduces the dimension of the problem by using the boundary integral formulation. Unfortunately, this advantage comes at a cost: it requires a fundamental solution to be known in order for the method to be applied. There are many linear problems for which fundamental solutions are not known: this is the case for the Poisson-Boltzmann equation with a heterogeneous permittivity inside the molecule, \emph{i.e.}
%
\begin{align} \label{eq:pbe_vp}
\nabla \cdot \left(\epsilon_1(\mathbf{x}) \nabla \phi_1(\mathbf{x})\right) &= \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) &&\mathbf{x} \in \Omega_1,\nonumber\\
\left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0 &&\mathbf{x}\in\Omega_2,\nonumber\\
\phi_1(\mathbf{x})  &= \phi_2(\mathbf{x}),&&\mathbf{x}\in \Gamma,\nonumber\\
\epsilon_1(\mathbf{x})\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x})  &= \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x}) &&\mathbf{x}\in \Gamma. 
\end{align}
%
A finite element method (FEM) is more suitable for such a case.

### 2023-09-20 results.tex
small edits

This section presents the verification and performance results of the presented FEM-BEM coupling schemes for molecules modelled as cavities with constant and varying permittivity.
With a constant permittivity inside the molecule, we tested convergence against an analytic expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
We also considered a Gaussian-varying permittivity\cite{grant2001smooth,li2013dielectric} inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.
The final tests show the scaling of the FEM-BEM coupling as the molecule size grows.

>>>>

This section presents the verification and performance results of the presented FEM-BEM coupling scheme for molecules modelled as cavities with constant and varying permittivity.
With a constant permittivity inside the molecule, we tested convergence against an analytic expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
Then, as a more challenging test, we performed binding energy calculations from a set of 153 structures,\cite{HarrisBoschitcshFenley2013} and compared them to well-established codes. 
We also considered a Gaussian-varying permittivity\cite{grant2001smooth,li2013dielectric} inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.
The final tests show the scaling of the FEM-BEM coupling as the molecule size grows.
